Wikipedia Text Mining and Entropy Analysis

### 2019-01-25 wiki_entropy/wiki_clustering.Rmd
rank models

```{r}
cosines <- wkpd %>%
  t() %>%
  cosine() %>%
  as_data_frame(rownames = "language1") %>%
  gather(language2, cosine, -language1)

@@

models <- wf_pairwise %>%
  group_by(feature) %>%
  nest() %>%
  mutate(model = map(data, ~glm(same ~ cosine, 
                                family = "binomial", data = .)))
```

>>>>

```{r}
cosines <- wkpd %>%
  column_to_rownames("Language") %>%
  t()%>%
  cosine() %>%
  as_data_frame(rownames = "language1") %>%
  gather(language2, cosine, -language1)

@@

models <- wf_pairwise %>%
  group_by(feature) %>%
  nest() %>%
  mutate(model = map(data, ~glm(same ~ cosine, 
                                family = "binomial", data = .)))

models %>%
  mutate(coeffs = map(model, tidy)) %>%
  select(-data, -model) %>%
  unnest() %>%
  filter(term == "cosine") %>%
  arrange(desc(statistic))
```
